The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
nobs proper interpret and cap

>>>>

<!-- RO first sentence... -->

(ref:nobs) : varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete dataset to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open. B) Mean connective redundancy across individuals increased with increasing number of observations, with a decreasing rate of increase around 100 observations. C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained sparse throughout for summer layers.

* common, though at different points - more observations until stabilizing
* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. * still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations

```{r, fig.cap='(ref:nobs)'}
knitr::include_graphics('../graphics/figure-nobs.png')
```
